NFC and burnout in teachers - A replication and extension study

### 2022-07-20 Manuscript/Revision_Letter.Rmd
answered age and covid burden

> This is a section quoted from the revised manuscript to illustrate the change.

\Assignment{JZ}
\AlmostDone
\Medium

@@

>>>>

\Assignment{JZ}
\Done

@@

We do not agree that this item justifies claims for a confounding of Covid burden and years of experience.
Firstly, years of experience cannot be equated with age, as some teachers are lateral entry employees.
Secondly, age itself is not the only risk factor for Covid, but one of a long list of risk factors according to the Center for Disease Control and Prevention, such as disability, asthma, cancer, chronic heart disease, diabetes, HIV, weak immune function, obesity, mental disorders, pregnancy, physical inactivity, etc.
Since the item does not specify the kind of risk factor, there is no need to correct for any confound between Covid burden and years of experience.

\Assignment{JZ}
\Done
